A comparison of classification algorithms applied to the Adult Database

### 2009-12-09 report/final.tex
nr of leaves and nodes for results.

\begin{table}[ht]
  \begin{center}
  \begin{tabular}{ | l | c | c | c |}
    \hline
    \textbf{Parameters} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} \\ \hline
    -U & 11.18 & 23.74 & 0m24.378s \\ \hline
    -C 0.05 & 15.67 & 22.86 & 0m24.414s \\ \hline
    -C 0.1 & 15.22 & 21.69 & 0m25.417s \\ \hline
    -C 0.15 & 14.85 & 22.25 & 0m25.086s \\ \hline
    -C 0.2 & 14.52 & 22.05 & 0m24.436s \\ \hline
    -C 0.25 & 14.40 & 22.08 & 0m24.628s \\ \hline
    -C 0.3 & 14.17 & 23.26 & 0m24.765s \\ \hline
    -C 0.35 & 13.84 & 22.42 & 0m25.154s \\ \hline
    -C 0.4 & 13.68 & 22.49 & 0m24.325s \\ \hline
    -C 0.45 & 13.26 & 22.43 & 0m25.086s \\ \hline
    -C 0.5 & 12.95 & 22.51 & 0m24.874s \\ \hline
    -C 0.55 & 11.19 & 24.94 & 0m25.899s \\ \hline
    -C 0.6 & 11.19 & 23.94 & 0m26.882s \\ \hline
    -C 0.7 & 11.19 & 23.94 & 0m26.638s \\ \hline
    -C 0.8 & 11.19 & 23.94 & 0m26.818s \\ \hline
    -C 0.9 & 11.19 & 23.94 & 0m26.634s \\ \hline
  \end{tabular}
  \caption{Results for C4.5.}
  \label{tbl:results_c45}
  \end{center}
\end{table}

>>>>

\begin{table}[ht]
  \begin{center}
  \begin{tabular}{ | l | c | c | c | c | c |}
    \hline
    \textbf{Parameters} & \textbf{Train error rate} & \textbf{Test error rate} & \textbf{Time} & \textbf{Nodes} & \textbf{Leaves} \\ \hline
    -U & 11.18 & 23.74 & 0m24.378s & 6919 & 6198 \\ \hline
    -C 0.05 & 15.67 & 22.86 & 0m24.414s & 46 & 38 \\ \hline
    -C 0.1 & 15.22 & 21.69 & 0m25.417s & 106 & 89 \\ \hline
    -C 0.15 & 14.85 & 22.25 & 0m25.086s & 186 & 158 \\ \hline
    -C 0.2 & 14.52 & 22.05 & 0m24.436s & 298 & 254 \\ \hline
    -C 0.25 & 14.40 & 22.08 & 0m24.628s & 376 & 319 \\ \hline
    -C 0.3 & 14.17 & 23.26 & 0m24.765s & 494 & 423 \\ \hline
    -C 0.35 & 13.84 & 22.42 & 0m25.154s & 692 & 593 \\ \hline
    -C 0.4 & 13.68 & 22.49 & 0m24.325s & 835 & 721 \\ \hline
    -C 0.45 & 13.26 & 22.43 & 0m25.086s & 1143 & 992 \\ \hline
    -C 0.5 & 12.95 & 22.51 & 0m24.874s & 1483 & 1292 \\ \hline
    -C 0.55 & 11.19 & 24.94 & 0m25.899s & 6727 & 6036 \\ \hline
    -C 0.6 & 11.19 & 23.94 & 0m26.882s & 6727 & 6036 \\ \hline
    -C 0.7 & 11.19 & 23.94 & 0m26.638s & 6727 & 6036 \\ \hline
    -C 0.8 & 11.19 & 23.94 & 0m26.818s & 6727 & 6036 \\ \hline
    -C 0.9 & 11.19 & 23.94 & 0m26.634s & 6727 & 6036 \\ \hline
  \end{tabular}
  \caption{Results for C4.5.}
  \label{tbl:results_c45}
  \end{center}
\end{table}
